---
title: '**REI Crunchbase Test_13**'
author: "YT"
date: 12/10/2019"
output:
  
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---


-- See Here: http://rpubs.com/TitelY/REICB -- 

```{r message=FALSE, warning=FALSE}

library(tidyverse) 
library(psych)
library(reshape2)
library(kableExtra)
library(knitr)
library(scales)
library(readxl)
library(highcharter)

```


**Limitations**

1. Exports limited to 1,000 observations
2. Many of the Technologies in the Trecker have no hits in Crunchbase
3. There is no time variable in the dataset

**KEYNAMES**

1     -     3D printing,
2     -     VR,
3     -     Drones,
4     -     IoT,
5     -     BIM


**General Variables**

1.  Tech	
2.  Organization
3.  Location	
4.  Categories
9.  CB Rank (Org & Person)


**IP Qwery Variables**

Patents, trademarks, IP Score - intellectual property holdings across multiple Patent and Trademark databases
10. IPqwery - Patents	Siftery - Total Products Active	CB Rank (Investor)
11. IPqwery - Trademarks Pending
12. IPqwery - Trademarks Registered
13. IPqwery - Trademarks	
14  IPqwery - Most Popular Patent Class
15. IPqwery - Patents Granted
16. IPqwery - Patents Pending	
17. IPqwery - IP Score

**Trend Variables**

18. Trend Score 
19. SimilarWeb - Monthly Visits	
20. BuiltWith - Tech Changes	


## Load data

```{r}
TechList <- read.csv("TECH_ALL_VR2.csv", na.strings=c(""," ","NA"))
#myData_new %>% View()
TechList %>% dim()
```

## Cleanup

```{r}

TechList =  subset(TechList, select = c(Tech,Last.Equity.Funding.Amount,Last.Funding.Date,Last.Funding.Amount.Currency..in.USD.)) 
TechList = na.omit(TechList)
TechList$Last.Funding.Date = as.Date(TechList$Last.Funding.Date)
VR= subset(TechList, Tech == "VR")

```


## Chart trend over time for one technology 

```{r}

Drone = subset(TechList, Tech == "Drone")

hc2 <- hchart(Drone, type = 'line', color = "#5cf740", hcaes(y = Last.Funding.Amount.Currency..in.USD., group = Tech, x = Last.Funding.Date)) %>%  
    hc_chart(backgroundColor = "black") %>% 

hc_tooltip(crosshairs = TRUE, borderWidth = 5, sort = TRUE, table = TRUE)  %>% 
    hc_title(text = "Last funding amount for Drone companies in the last 10 years") %>% 
    hc_subtitle(text = "Crunchbase exploratory funding over time")
hc2
```


## Week_03
## Extend search for all technologies - for products and processes

****************************************************************************************************************
Process and Product - entire list 
****************************************************************************************************************

## Process 


```{r}
Process <- read.csv("process.csv", na.strings=c(""," ","NA"))
#myData %>% View()
Process %>% dim()
```

```{r}
Process
```

## Chart 

```{r}

# Process


hc2 <- hchart(Process, type = 'column',  color = "#B71C1C", borderWidth = 0, hcaes( x = Technology, y = Companies)) %>%  
    hc_chart(backgroundColor = "black") %>% 

hc_tooltip(crosshairs = TRUE, borderWidth = 5, sort = TRUE, table = TRUE)  %>% 
    hc_title(text = "Tehnology Process - how many companies come up on CrunchBase") %>% 
    hc_subtitle(text = "Crunchbase data test version 02")

hc2

```

## Results 

****************************************************************************************************************
**Process** Results - 4 out of 42 technologies have companies associated with them on Crunchbase
****************************************************************************************************************


```{r}
Products <- read.csv("product.csv", na.strings=c(""," ","NA"))
```

## Products   

```{r}
Products
```


```{r}

# Products


hc2 <- hchart(Products, type = 'column',  borderWidth = 0, hcaes( x = Technology, y = Companies)) %>%  
    hc_chart(backgroundColor = "black") %>% 

hc_tooltip(crosshairs = TRUE, borderWidth = 5, sort = TRUE, table = TRUE)  %>% 
    hc_title(text = "Tehnology Products - how many companies come up on CrunchBase") %>% 
    hc_subtitle(text = "Crunchbase data test version 02")

hc2
```

## Results 

******************************************************************************************************************Products** Results - 7 out of 55 technologies have companies associated with them on Crunchbase ***************************************************************************************************************************************************************************************************************************************************************************************************************************************************************************************************************************************************************


## addendum - questions 

*******************************************
## Which technologies are in this dataset:
*******************************************


## Which technologies are in this dataset:

```{r}
myData <- read.csv("techtext_v5.csv", na.strings=c(""," ","NA"))

```


```{r}
  
## Observation #1 - dataset limited to 1,000 roes,
## Observation #2 - BIM has only 473 results.  

hchart((myData$Tech),  color = "#B71C1C", borderWidth = 2, borderColor  = "#B71C1C", name = "# companies", color = 'Tech') %>%  
    hc_chart(backgroundColor = "black") %>% 
    hc_size(height = 600) %>% 

hc_tooltip(crosshairs = TRUE, borderWidth = 5, sort = TRUE, table = TRUE)  %>% 
    hc_title(text = "Number of Technolegies in dataset") %>% 
    hc_subtitle(text = "Crunchbase data test version 01")

```

## What **type** of companies are these?


```{r}

# distribution - top industrues are 3D printing (69) and Drones (51)

hchart((myData$Categories),  color = "#B71C1C", borderWidth = 2, borderColor  = "#B71C1C", name = "# listings", color = 'city') %>%  
    hc_chart(backgroundColor = "black") %>% 
    hc_size(height = 600) %>% 

hc_tooltip(crosshairs = TRUE, borderWidth = 5, sort = TRUE, table = TRUE)  %>% 
    hc_title(text = "Companny Type") %>% 
    hc_subtitle(text = "Distribution of the type of company")

```


## Where are these companies located:

```{r}

# Answer: London, NYC and SF.

hchart((myData$Location),  color = "#B71C1C", borderWidth = 2, borderColor  = "#B71C1C", name = "Locations", color = 'city') %>%  
    hc_chart(backgroundColor = "black") %>% 
    hc_size(height = 600) %>% 

hc_tooltip(crosshairs = TRUE, borderWidth = 5, sort = TRUE, table = TRUE)  %>% 
    hc_title(text = "Company distribution by Location") %>% 
    hc_subtitle(text = "Distribution of all locations by company")

```

## Service distribution


```{r}
### Service type with Siftery 
hchart((myData$Siftery...Total.Products.Active),  color = "#B71C1C", borderWidth = 2, borderColor  = "#B71C1C", name = "# Services", color = 'Tech') %>%  
    hc_chart(backgroundColor = "black") %>% 
    hc_size(height = 600) %>% 

hc_tooltip(crosshairs = TRUE, borderWidth = 5, sort = TRUE, table = TRUE)  %>% 
    hc_title(text = "Number of Technolegies in dataset") %>% 
    hc_subtitle(text = "Crunchbase data test version 01")

```

## What is the distribution of IQ scores

```{r}
### IP score analysis - webbease app 

hchart((myData$IPqwery...IP.Score),   color = "#B71C1C", borderWidth = 2, borderColor  = "#B71C1C", name = "IP", color = 'Tech') %>%  
    hc_chart(backgroundColor = "black") %>% 
    hc_size(height = 600) %>% 

hc_tooltip(crosshairs = TRUE, borderWidth = 5, sort = TRUE, table = TRUE)  %>% 
    hc_title(text = "Number of Technolegies in dataset") %>% 
    hc_subtitle(text = "Crunchbase data test version 01")

```





























